\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\begin{thebibliography}{100}
\bibliographystyle{IEEEtran}

\bibitem{sgraph}
H. Chen, M. Zhang, K. Yang, et al., ``Achieving Sub-second Pairwise Query over Evolving Graphs,'' in \textit{Proceedings of the 28th ACM International Conference on Architectural Support for Programming Languages and Operating Systems}, 2023, pp. 1--15.

\bibitem{tripoline}
X. Jiang, C. Xu, X. Yin, et al., ``Tripoline: generalized incremental graph processing via graph triangle inequality,'' in \textit{Proceedings of the Sixteenth European Conference on Computer Systems}, 2021, pp. 17--32.

\bibitem{pnp}
C. Xu, K. Vora, R. Gupta, ``Pnp: Pruning and prediction for point-to-point iterative graph analytics,'' in \textit{Proceedings of the Twenty-Fourth International Conference on Architectural Support for Programming Languages and Operating Systems}, 2019, pp. 587--600.

\bibitem{aligroup}
``Alibaba Group,'' https://www.alibabagroup.com/document-1595215205757878272, 2023.


\bibitem{google}
``Google Maps,'' https://www.alibabagroup, 2023.

\bibitem{facebook}
``Facebook,'' www.facebook.com, 2023.

\bibitem{alipay}
``Alipay,'' www.alipay.com, 2019.

\bibitem{cagis}
``Cagis,'' http://www.cagis.org.cn, 2021.

\bibitem{baidu}
``Baidu Baike,'' https://baike.baidu.com, 2023.

\bibitem{amap}
``A Map,'' https://ditu.amap.com, 2023.

\bibitem{qq}
``Tencent Maps,'' https://map.qq.com, 2023.

\bibitem{petalmaps}
``Petal Maps,'' https://www.petalmaps.com, 2023.

\bibitem{gemini}
X. Zhu, W. Chen, W. Zheng, et al., ``Gemini: A {Computation-Centric} Distributed Graph Processing System,'' in \textit{12th USENIX Symposium on Operating Systems Design and Implementation}, 2016, pp. 301--316.

\bibitem{giraph}
C. Avery, ``Giraph: Large-scale graph processing infrastructure on hadoop,'' in \textit{Proceedings of the Hadoop Summit}, pp. 5--9, 2011.

\bibitem{graphlab}
Y. Low, J. Gonzalez, A. Kyrola, et al., ``Graphlab: A new framework for parallel machine learning,'' \textit{arXiv preprint arXiv:1408.2041}, 2019.

\bibitem{powergraph}
J. Gonzalez, Y. Low, H. Gu, et al., ``{PowerGraph}: Distributed {Graph-Parallel} Computation on Natural Graphs,'' in \textit{10th USENIX symposium on operating systems design and implementation}, 2012, pp. 17--30.

\bibitem{graphx}
J. Gonzalez, R. Xin, A. Dave, et al., ``{GraphX}: Graph Processing in a Distributed Dataflow Framework,'' in \textit{11th USENIX symposium on operating systems design and implementation}, 2014, pp. 599--613.

\bibitem{soa}
C. Xie, R. Chen, H. Guan, et al., ``Sync or async: Time to fuse for distributed graph-parallel computation,'' \textit{ACM SIGPLAN Notices}, vol. 50, no. 8, pp. 194--204, 2015.

\bibitem{powerlyra}
R. Chen, J. Shi, Y. Chen, et al., ``Powerlyra: Differentiated graph computation and partitioning on skewed graphs,'' \textit{ACM Transactions on Parallel Computing}, vol. 5, no. 3, pp. 1--39, 2019.

\bibitem{snap}
``Stanford large network dataset collection,'' http://snap.stanford.edu/data/index.html, 2020.

\bibitem{twitter}
H. Kwak, C. Lee, H. Park, et al., ``What is Twitter, a social network or a news media?'' in \textit{Proceedings of the 19th international conference on World wide web}, 2020, pp. 591--600.

\bibitem{bubing}
P. Boldi, A. Marino and M. Santini, et al.,  ``BUbiNG: Massive Crawling for the Masses,''  \textit{ACM Transactions on the Web}, vol. 12, no. 2, pp. 1--26, 2018.

\bibitem{timeaware}
P. Boldi, M. Santini and S. Vigna,  ``A large time-aware web graph,''  \textit{ACM SIGIR Forum}, vol. 42, no. 2, pp. 33--38, 2008.

\bibitem{ligra}
J. Shun, J. Blelloch, ``Ligra: a lightweight graph processing framework for shared memory,'' in \textit{Proceedings of the 18th ACM SIGPLAN symposium on Principles and practice of parallel programming}, 2013, pp. 135--146.

\bibitem{kickstarter}
K. Vora, R. Gupta, G. Xu, ``Kickstarter: Fast and accurate computations on streaming graphs via trimmed approximations,'' in \textit{Proceedings of the twenty-second international conference on architectural support for programming languages and operating systems}, 2017, pp. 237--251.

\bibitem{graphbolt}
M. Mariappan, K. Vora, ``Graphbolt: Dependency-driven synchronous processing of streaming graphs,'' in \textit{Proceedings of the Fourteenth EuroSys Conference 2019}, 2019, pp. 1--16.

\bibitem{digraph}
Y. Zhang, X. Liao, H. Jin, et al., ``DiGraph: An efficient path-based iterative directed graph processing system on multiple GPUs,'' in \textit{Proceedings of the Twenty-Fourth International Conference on Architectural Support for Programming Languages and Operating Systems}, 2019, pp. 601--614.

\bibitem{lccg}
J. Zhao, Y. Zhang, X. Liao, et al., ``LCCG: A Locality-Centric Hardware Accelerator for High Throughput of Concurrent Graph Processing,'' in \textit{SC21: International Conference for High Performance Computing, Networking, Storage and Analysis}, 2021, pp. 1--14.

\bibitem{depgraph}
Y. Zhang, X. Liao, H. Jin, et al., ``DepGraph: A Dependency-Driven Accelerator for Efficient Iterative Graph Processing,'' in \textit{2021 IEEE International Symposium on High-Performance Computer Architecture }, 2021, pp. 371--384.

\bibitem{tdgraph}
J. Zhao, Y. Yang, Y. Zhang, et al., ``TDGraph: a topology-driven accelerator for high-performance streaming graph processing,'' in \textit{Proceedings of the 49th Annual International Symposium on Computer Architecture.}, 2022, pp. 116--129.

\bibitem{graphchi}
A. Kyrola, G. Blelloch, C. Guestrin, ``{GraphChi}:{Large-Scale} Graph Computation on Just a {PC},'' in \textit{Proceedings of the 10th USENIX Symposium on Operating Systems Design and Implementation}, 2012, pp. 31--46.

\bibitem{x-stream}
A. Roy, I. Mihailovic, W. Zwaenepoel,  ``X-stream: Edge-centric graph processing using streaming partitions,'' in \textit{Proceedings of the Twenty-Fourth ACM Symposium on Operating Systems Principles}, 2013, pp. 472--488.

\bibitem{flashgraph}
D. Zheng, M. Mhembere, R. Burns, et al., ``{FlashGraph}: Processing {Billion-Node} Graphs on an Array of Commodity {SSDs},'' in \textit{13th USENIX Conference on File and Storage Technologies}, 2015, pp. 45--58.

\bibitem{gridgraph}
X. Zhu, W. Han, W. Chen, ``{GridGraph}:{Large-Scale} Graph Processing on a Single Machine Using 2-Level Hierarchical Partitioning,'' in \textit{2015 USENIX Annual Technical Conference }, 2015, pp. 375--386.

\bibitem{efficient}
Y. Zhang, X. Liao, X. Shi, et al., ``Efficient Disk-Based Directed Graph Processing: A Strongly Connected Component Approach,'' \textit{IEEE Transactions on Parallel and Distributed Systems}, vol. 29, no. 4, pp. 830--842, 2018.

\bibitem{graphm}
J. Zhao, Y. Zhang, X. Liao, et al., ``GraphM: an efficient storage system for high throughput of concurrent graph processing,'' in \textit{Proceedings of the International Conference for High Performance Computing, Networking, Storage and Analysis}, 2019, pp. 1--14.

\bibitem{pregel}
G. Malewicz, M. Austern, A. Bik, et al., ``Pregel: a system for large-scale graph processing,'' in \textit{Proceedings of the 2010 ACM SIGMOD International Conference on Management of data}, 2010, pp. 135--146.

\bibitem{cgraph}
Y. Zhang, J. Zhao, X. Liao, et al., ``{CGraph}: A Correlations-aware Approach for Efficient Concurrent Iterative Graph Processing,'' in \textit{2018 USENIX Annual Technical Conference }, 2018, pp. 441--452.

\bibitem{hub}
R. Jin, N. Ruan, B. You, et al., ``Hub-accelerator: Fast and exact shortest path computation in large social networks,'' \textit{arXiv preprint arXiv:1305.0507}, 2013.

\bibitem{quegel}
Q. Zhang, D. Yan and J. Cheng, ``Quegel: A general-purpose system for querying big graphs,'' in \textit{Proceedings of the 2016 International Conference on Management of Data}, 2016, pp. 2189--2192.

\bibitem{Congra}
P. Pan and C. Li, ``Congra: Towards Efficient Processing of Concurrent Graph Queries on Shared-Memory Machines,'' in \textit{2017 IEEE International Conference on Computer Design}, 2017, pp. 217--224.

\bibitem{krill}
H. Chen, M. Shen, N. Xiao, et al., ``Krill: a compiler and runtime system for concurrent graph processing,'' in \textit{Proceedings of the International Conference for High Performance Computing, Networking, Storage and Analysis}, 2021, pp. 1--16.

\bibitem{cache}
S. Lu, S. Sun, J. Paul, et al., ``Cache-efficient fork-processing patterns on large graphs,'' in \textit{Proceedings of the 2021 International Conference on Management of Data}, 2021, pp. 1208--1221.

\bibitem{seraph}
J. Xue, Z. Yang, Z. Qu, et al., ``Seraph: an efficient, low-cost system for concurrent graph processing,'' in \textit{Proceedings of the 23rd international symposium on High-performance parallel and distributed computing}, 2014, pp. 227--238.

\bibitem{multilyra}
A. Mazloumi, X. Jiang, R. Gupta, ``Multilyra: Scalable distributed evaluation of batches of iterative graph queries,'' in \textit{2019 IEEE International Conference on Big Data }, 2019, pp. 349--358.

\bibitem{bead}
A. Mazloumi, C. Xu, Z. Zhao, et al., ``BEAD: Batched Evaluation of Iterative Graph Queries with Evolving Analytics Demands,'' in \textit{2020 IEEE International Conference on Big Data}, 2020, pp. 461--468.




\end{thebibliography}






\end{document}


