\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\begin{document}

\begin{thebibliography}{100}
\bibliographystyle{IEEEtran}

\bibitem{sgraph}
H. Chen, M. Zhang, K. Yang, et al., ``Achieving Sub-second Pairwise Query over Evolving Graphs,'' in \textit{Proc. Int. Conf. Architectural Support Program. Languages Operating Syst.}, Vancouver, BC, Canada, 2023, pp. 1--15.

\bibitem{tripoline}
X. Jiang, C. Xu, X. Yin, et al., ``Tripoline: generalized incremental graph processing via graph triangle inequality,'' in \textit{Proc. Eur. Conf. Comput. Syst.}, United Kingdom, 2021, pp. 17--32.

\bibitem{pnp}
C. Xu, K. Vora, R. Gupta, ``Pnp: Pruning and prediction for point-to-point iterative graph analytics,'' in \textit{Proc. Int. Conf. Architectural Support Program. Languages Operating Syst.}, Providence, RI, USA, 2019, pp. 587--600.

\bibitem{aligroup}
``Alibaba Group,'' https://www.alibabagroup.com/document-1595215205757878272, 2023.


\bibitem{google}
``Google Maps,'' https://www.alibabagroup, 2023.

\bibitem{facebook}
``Facebook,'' www.facebook.com, 2023.

\bibitem{alipay}
``Alipay,'' www.alipay.com, 2019.

\bibitem{cagis}
``Cagis,'' http://www.cagis.org.cn, 2021.

\bibitem{baidu}
``Baidu Baike,'' https://baike.baidu.com, 2023.

\bibitem{amap}
``A Map,'' https://ditu.amap.com, 2023.

\bibitem{qq}
``Tencent Maps,'' https://map.qq.com, 2023.

\bibitem{petalmaps}
``Petal Maps,'' https://www.petalmaps.com, 2023.

\bibitem{gemini}
X. Zhu, W. Chen, W. Zheng, et al., ``Gemini: A {Computation-Centric} Distributed Graph Processing System,'' in \textit{USENIX Symp. Operating Syst. Des. Implementation}, Savannah, GA, USA, 2016, pp. 301--316.

\bibitem{giraph}
C. Avery, ``Giraph: Large-scale graph processing infrastructure on hadoop,'' in \textit{Proc. Hadoop Summit}, pp. 5--9, 2011.

\bibitem{graphlab}
Y. Low, J. Gonzalez, A. Kyrola, et al., ``Graphlab: A new framework for parallel machine learning,'' \textit{arXiv preprint arXiv:1408.2041}, 2019.

\bibitem{powergraph}
J. Gonzalez, Y. Low, H. Gu, et al., ``{PowerGraph}: Distributed {Graph-Parallel} Computation on Natural Graphs,'' in \textit{USENIX Symp. Operating Syst. Des. Implementation}, Hollywood, CA, USA, 2012, pp. 17--30.

\bibitem{graphx}
J. Gonzalez, R. Xin, A. Dave, et al., ``{GraphX}: Graph Processing in a Distributed Dataflow Framework,'' in \textit{USENIX Symp. Operating Syst. Des. Implementation}, Broomfield, CO, USA, 2014, pp. 599--613.

\bibitem{soa}
C. Xie, R. Chen, H. Guan, et al., ``Sync or async: Time to fuse for distributed graph-parallel computation,'' \textit{ACM SIGPLAN Notices}, vol. 50, no. 8, pp. 194--204, 2015.

\bibitem{powerlyra}
R. Chen, J. Shi, Y. Chen, et al., ``Powerlyra: Differentiated graph computation and partitioning on skewed graphs,'' \textit{ACM Trans. Parallel Comput.}, vol. 5, no. 3, pp. 1--39, 2019.

\bibitem{snap}
``Stanford large network dataset collection,'' http://snap.stanford.edu/data/index.html, 2020.

\bibitem{twitter}
H. Kwak, C. Lee, H. Park, et al., ``What is Twitter, a social network or a news media?'' in \textit{Proc. Int. Conf. World Wide Web}, Raleigh, NC, USA, 2020, pp. 591--600.

\bibitem{bubing}
P. Boldi, A. Marino and M. Santini, et al.,  ``BUbiNG: Massive Crawling for the Masses,''  \textit{ACM Trans. Web}, vol. 12, no. 2, pp. 1--26, 2018.

\bibitem{timeaware}
P. Boldi, M. Santini and S. Vigna,  ``A large time-aware web graph,''  \textit{ACM SIGIR Forum}, vol. 42, no. 2, pp. 33--38, 2008.

\bibitem{ligra}
J. Shun, J. Blelloch, ``Ligra: a lightweight graph processing framework for shared memory,'' in \textit{Proc. Symp. Princ. Pract. Parallel Program.}, Shenzhen, China, 2013, pp. 135--146.

\bibitem{kickstarter}
K. Vora, R. Gupta, G. Xu, ``Kickstarter: Fast and accurate computations on streaming graphs via trimmed approximations,'' in \textit{Proc. Int. Conf. Architectural Support Program. Languages Operating Syst.}, New York, NY, USA, 2017, pp. 237--251.

\bibitem{graphbolt}
M. Mariappan, K. Vora, ``Graphbolt: Dependency-driven synchronous processing of streaming graphs,'' in \textit{Proc. EuroSys Conf.}, Dresden , Germany, 2019, pp. 1--16.

\bibitem{digraph}
Y. Zhang, X. Liao, H. Jin, et al., ``DiGraph: An efficient path-based iterative directed graph processing system on multiple GPUs,'' in \textit{Proc. Int. Cinf. Architectural Support Program. Languages and Operating Syst.}, Providence, RI, USA, 2019, pp. 601--614.

\bibitem{lccg}
J. Zhao, Y. Zhang, X. Liao, et al., ``LCCG: A Locality-Centric Hardware Accelerator for High Throughput of Concurrent Graph Processing,'' in \textit{Int. Conf. High Perform. Comput., Netw., Storage Anal.}, New York, NY, USA, 2021, pp. 1--14.

\bibitem{depgraph}
Y. Zhang, X. Liao, H. Jin, et al., ``DepGraph: A Dependency-Driven Accelerator for Efficient Iterative Graph Processing,'' in \textit{IEEE Int. Symp. High-Perform. Comput. Architecture }, Seoul, Korea, 2021, pp. 371--384.

\bibitem{tdgraph}
J. Zhao, Y. Yang, Y. Zhang, et al., ``TDGraph: a topology-driven accelerator for high-performance streaming graph processing,'' in \textit{Proc. Annu. Int. Symp. Comput. Architecture}, New York, NY, USA, 2022, pp. 116--129.

\bibitem{graphchi}
A. Kyrola, G. Blelloch, C. Guestrin, ``{GraphChi}:{Large-Scale} Graph Computation on Just a {PC},'' in \textit{Proc. USENIX Symp. Operating Syst. Des. Implementation}, Hollywood, CA, USA, 2012, pp. 31--46.

\bibitem{x-stream}
A. Roy, I. Mihailovic, W. Zwaenepoel,  ``X-stream: Edge-centric graph processing using streaming partitions,'' in \textit{Proc. ACM Symp. Operating Syst. Princ.}, Farminton, Pennsylvania, USA, 2013, pp. 472--488.

\bibitem{flashgraph}
D. Zheng, M. Mhembere, R. Burns, et al., ``{FlashGraph}: Processing {Billion-Node} Graphs on an Array of Commodity {SSDs},'' in \textit{USENIX Conf. File Storage Technologies}, Santa Clara, CA, USA, 2015, pp. 45--58.

\bibitem{gridgraph}
X. Zhu, W. Han, W. Chen, ``{GridGraph}:{Large-Scale} Graph Processing on a Single Machine Using 2-Level Hierarchical Partitioning,'' in \textit{USENIX Annu. Tech. Conf.}, Santa Clara, CA, USA, 2015, pp. 375--386.

\bibitem{efficient}
Y. Zhang, X. Liao, X. Shi, et al., ``Efficient Disk-Based Directed Graph Processing: A Strongly Connected Component Approach,'' \textit{IEEE Trans. Parallel Distrib. Syst.}, vol. 29, no. 4, pp. 830--842, 2018.

\bibitem{graphm}
J. Zhao, Y. Zhang, X. Liao, et al., ``GraphM: an efficient storage system for high throughput of concurrent graph processing,'' in \textit{Proc. Int. Conf. High Perform. Comput., Netw., Storage and Anal.}, Denver, Colorado, USA, 2019, pp. 1--14.

\bibitem{pregel}
G. Malewicz, M. Austern, A. Bik, et al., ``Pregel: a system for large-scale graph processing,'' in \textit{Proc. ACM SIGMOD Int. Conf. Manage. Data}, New York, NY, USA, 2010, pp. 135--146.

\bibitem{cgraph}
Y. Zhang, J. Zhao, X. Liao, et al., ``{CGraph}: A Correlations-aware Approach for Efficient Concurrent Iterative Graph Processing,'' in \textit{USENIX Annu. Tech. Conf.}, Boston, MA, USA, 2018, pp. 441--452.

\bibitem{hub}
R. Jin, N. Ruan, B. You, et al., ``Hub-accelerator: Fast and exact shortest path computation in large social networks,'' \textit{arXiv preprint arXiv:1305.0507}, 2013.

\bibitem{quegel}
Q. Zhang, D. Yan and J. Cheng, ``Quegel: A general-purpose system for querying big graphs,'' in \textit{Proc. Int. Conf. Manage. Data}, New York, NY, USA, 2016, pp. 2189--2192.

\bibitem{Congra}
P. Pan and C. Li, ``Congra: Towards Efficient Processing of Concurrent Graph Queries on Shared-Memory Machines,'' in \textit{IEEE Int. Conf. Comput. Des.}, Boston, MA, USA, 2017, pp. 217--224.

\bibitem{krill}
H. Chen, M. Shen, N. Xiao, et al., ``Krill: a compiler and runtime system for concurrent graph processing,'' in \textit{Proc. Int. Conf. High Perform. Comput., Netw., Storage and Anal.}, New York, NY, USA, 2021, pp. 1--16.

\bibitem{cache}
S. Lu, S. Sun, J. Paul, et al., ``Cache-efficient fork-processing patterns on large graphs,'' in \textit{Proc. Int. Conf. Manage. Data}, New York, NY, USA, 2021, pp. 1208--1221.

\bibitem{seraph}
J. Xue, Z. Yang, Z. Qu, et al., ``Seraph: an efficient, low-cost system for concurrent graph processing,'' in \textit{Proc. Int. Symp. High-perform. Parallel Distrib. Comput.}, Vancouver, BC, Canada, 2014, pp. 227--238.

\bibitem{multilyra}
A. Mazloumi, X. Jiang, R. Gupta, ``Multilyra: Scalable distributed evaluation of batches of iterative graph queries,'' in \textit{IEEE Int. Conf. Big Data}, Los Angeles, CA, USA, 2019, pp. 349--358.

\bibitem{bead}
A. Mazloumi, C. Xu, Z. Zhao, et al., ``BEAD: Batched Evaluation of Iterative Graph Queries with Evolving Analytics Demands,'' in \textit{IEEE Int. Conf. Big Data}, 2020, pp. 461--468.

\bibitem{r3}
H. Wang, G. Li, H. Hu, et al., ``R3: a real-time route recommendation system,'' \textit{Proc. VLDB Endowment}, vol. 7,no. 13, pp. 1549--1552, 2014.

\bibitem{recommender}
Q. Guo, F. Zhuang, C. Qin, et al., ``A Survey on Knowledge Graph-Based Recommender Systems,'' \textit{IEEE Trans. Knowl. Data Eng.}, vol. 34, no. 8, pp. 3549--3568, 2020.


\bibitem{news}
K. Joseph, H. Jiang, ``Content based News Recommendation via Shortest Entity Distance over Knowledge Graphs,'' in \textit{Companion Proc. 2019 World Wide Web Conf.}, San Francisco, CA, USA, 2019, pp. 690--699.

\bibitem{capacity}
M. Pollack, ``The maximum capacity through a network,'' \textit{Operations Res.}, Vol. 8, no. 5, pp. 733--736, 1960.

\bibitem{optimal}
O. Berman, G. Handler, ``Optimal Minimax Path of a Single Service Unit on a Network to Nonservice Destinations,'' \textit{Transp. Sci.}, Vol. 21, no. 2, pp. 115--122, 1987.

\bibitem{2-hop}
E. Cohen, E. Halperin, H. Kaplan, et al., ``Reachability and Distance Queries via 2-Hop Labels,'' \textit{SIAM J. Comput.}, Vol. 32, no. 5, pp. 1338--1355, 2003.

\bibitem{improved}
L. Roditty, U. Zwick, ``Improved Dynamic Reachability Algorithms for Directed Graphs,'' \textit{SIAM J. Comput.}, Vol. 37, no. 5, pp. 1455--1471, 2008.

\bibitem{large}
A. Zhu, W. Lin, S. Wang, et al., ``Reachability Queries on Large Dynamic Graphs: A Total Order Approach,'' in \textit{Proc. ACM SIGMOD Int. Conf. Manage. Data}, Snowbird, UT, USA, 2014, pp.1323--1334.

\bibitem{framework}
L. Dhulipala, C. Hong, J. Shun, ``A framework for static and incremental parallel graph connectivity algorithms,'' \textit{arXiv preprint arXiv:2008.03909}, 2020.


\end{thebibliography}






\end{document}


